---
title: "Data prepreation"

output: 
  html_document: 
    toc: yes
    theme: cerulean
---


#  Mapping AfD election results in German Wahlkreise

```{r}
library(sf)
library(stringr)
library(tidyverse)
library(readxl)
library(magrittr)
library(huxtable)
library(broom)
```



## Geo data
```{r setup, include=FALSE}
my_path_wahlkreise <- "~/Documents/Github/R-Prediction/btw21_geometrie_wahlkreise_shp/Geometrie_Wahlkreise_20DBT.shp"
file.exists(my_path_wahlkreise)
```

```{r}
wahlkreise_shp <- st_read(my_path_wahlkreise)
```

```{r}
glimpse(wahlkreise_shp)
```



## data

```{r}
data <- "~/Documents/Github/R-Prediction/btw21_Strukturdaten.csv"

file.exists(data)
```


```{r}
data_raw <- read_delim(data,
    ";", escape_double = FALSE,
    locale = locale(decimal_mark = ",",
        grouping_mark = "."),
    trim_ws = TRUE,
    skip = 8)  # skipt the first 8 rows
```


we need to do some cleansing before we can work with this dataset.

```{r}
data_names <- names(data_raw)

data_de <- data_raw

names(data_de) <- paste0("V",1:ncol(data_de))
```
The important columns are:



The important columns are:
```{r}
data_de <- data_de %>%
  rename(state = V1,
         area_nr = V2,
         area_name = V3,
         total_n = V6,
         germans_n = V7,
         for_prop = V8,
         pop_move_prop = V11,
         pop_migr_background_prop = V19,
         income = V26,
         unemp_prop = V47)
```


Compute some more columns and remove missing vlaues:

```{r socec-new-cols}
data_de <- data_de %>% 
   mutate(foreigner_n = total_n - germans_n,
         pop_move_n = pop_move_prop * total_n,
         unemp_n = unemp_prop * total_n / 100,
         pop_migr_background_n = pop_migr_background_prop * total_n / 100) %>% 
  drop_na()
```





## AfD election results





```{r}
elec_results = read.csv2("~/Documents/Github/R-Prediction/kerg.csv", head = TRUE, sep="\t")
```


```{r}
head(elec_results)
```


Same thing with the election data, here we only need the criterion (AfD success) and the ID variables for merging:

```{r elec-results-new-cols}
elec_results2 <- elec_results %>%
  rename(afd_votes = AfD3,
         area_nr = Nr,
         area_name = Gebiet,
         votes_total = Waehler_gueltige_Zweitstimmen_vorlauefig) %>% 
   mutate(afd_prop = afd_votes/votes_total)    # valid votes only, and of the present Zweitstimme
```

Note that we are focusing on the Zweitstimme of the present election (hence the `3` in `votes_valid_3` and in `AfD_3`).


Note that we are focusing on the Zweitstimme of the present election (hence the `3` in `votes_valid_3` and in `AfD_3`).

# Merge/Join socec data with election data


```{r merge}
data_de %>%
  left_join(elec_results2, by = "area_name") %>% 
  left_join(wahlkreise_shp, by = c("area_name" = "WKR_NAME")) -> d_all_with_na
```




## After-merge preparations



Add variable for East (1) vs. West (0):


```{r east-west-dummy}
d_all_with_na <- d_all_with_na %>% 
  mutate(east = case_when(
    state %in% c("Mecklenburg-Vorpommern", "Brandenburg", "Berlin", "Sachsen-Anhalt", "Sachsen", "Thüringen") ~ "yes",
    TRUE ~ "no"
    ) 
  )

d_all_with_na$east_num <- ifelse(d_all_with_na$east == "yes", 1, 0)
```



## Main data frame: d_short 

We will also provide a version without the geo data, and in pure (old school) `data frame` form (ie., not as tibble)_

```{r d-short-with-nas}
d_all_with_na %>%
  rename(area_nr = area_nr.x) %>% 
  select(state,
         area_nr,
         area_name,
         total_n,
         germans_n,
         foreigner_n,
         for_prop,
         pop_move_n,
         pop_migr_background_n,
         income ,
         unemp_n,
         unemp_prop,
         votes_total,
         afd_votes,
         afd_prop,
         state,
         east,
         east_num) -> d_short_with_nas


```





Remove NAs:

```{r nona}
d_short_with_nas %>% 
  drop_na() -> d_short_nona
```


Add state id:

```{r staste-id}
d_short_nona$state_id <- coerce_index(d_short_nona$state)

```


Create dictionnary for state id:

```{r state-dict} 
state_dict <- d_short_nona %>% 
  distinct(state_id, .keep_all = TRUE) %>% 
  select(state_id, state)
```



Multiply by 1000 to get the real numbers so that a count model gets the "right" data

```{r mult-by-1000}
d_short_nona %>%
  mutate_at(vars(total_n, germans_n, foreigner_n, pop_move_n,
                    pop_migr_background_n, unemp_n), funs(. * 1000)
  ) -> d_short_nona_1000

if (params$verbose == TRUE) glimpse(d_short_nona_1000)

```


```{r}
View(d_short_nona)
```

